Parsing Postfix log files

### 2008-02-26 doc/logparser.tex
Documented new valid combo. Improved introduction, referring to the new content, and pointing out novel     things.  Needs more work, I think.

Section~\ref{background} provides background information useful in
understanding the paper, parser and algorithm.

This algorithm requires a database for storing both the rules used when
parsing and the results gleaned from parsing.  The database schema used is
described in section~\ref{database schema}, explaining in detail the tables
used for storing the data gleaned from the logs and the table that stores
the rules.

Section~\ref{rules} discusses the parsing rules in detail, explaining the
purpose and usage of each field in a rule, referring to an example rule and
sample data it matches successfully against.  This section concludes with a
discussion of rule efficiency concerns.

Section~\ref{parsing-algorithm} contains the meat of the paper, describing
a naive parsing algorithm and the complications encountered which shaped
the full algorithm, followed by a comprehensive explanation of the
different stages of the algorithm, the actions taken during execution of
the algorithm, and further complications whose solution completes the
algorithm.

Section~\ref{parsing coverage} analyses the coverage the parser achieves
over a set of \numberOFlogFILES{} log files taken from a mail server
handling mail for over 1000 users.  Coverage is described both in terms of
the fraction of lines parsed and the fraction of mails and connections
successfully reconstructed by the parsing algorithm, including dealing with
false negatives and a discussion of the difficulties in identifying false
positives.

Section~\ref{limitations-improvements} lists the limitations of the
algorithm, then suggests some ways of dealing with the limitations, with
the goal of improving parsing and reproduction of the journey a mail takes
through Postfix.

Section~\ref{conclusion} is contains the paper's conclusion.

@@

The bibliography contains references to the resources used in developing
the algorithm, writing the program and preparing this paper.  Also listed
are some additional resources expected to be helpful in understanding
\SMTP{}, Postfix, anti-spam techniques, or the paper.

Appendix~\ref{graphs} contains graphs illustrating the topics previously
discussed in section~\ref{rule efficiency}, rule efficiency, and explains
the irregularities observed in these graphs.

@@

>>>>

Section~\ref{background} provides background information useful in
understanding the paper, parser and algorithm.  It introduces the idea of
using a database schema as an \API{}, providing an interface to the data
gathered that is language-neutral.  The unusual separation of rules,
actions and algorithm is discussed, giving the reasons that approach was
taken when designing the parser.

This algorithm requires a database for storing both the rules used when
parsing and the results gleaned from parsing.  The database schema used is
described in \sectionref{database schema}, explaining in detail the tables
used for storing the data gleaned from the logs and the table that stores
the rules.

Section~\ref{rules} discusses the parsing rules in detail, explaining the
purpose and usage of each field in a rule, referring to an example rule and
sample data it matches successfully against.  The pros and cons of
overlapping rules are discussed, including techniques for detecting
unintentional overlaps.  Rule efficiency concerns are discussed, in
particular the optimisations used by the algorithm, with reference to the
graphs in appendix~\refwithpage{graphs}.  The final section is a
description of using the tools provided with the parser to generate a
\regex{} from related log lines for new rules.

Section~\ref{parsing-algorithm} contains the core of the paper, describing
a naive parsing algorithm and the complications encountered which shaped
the full algorithm.  A flow chart and a discussion of the emergent
behaviour exhibited by the algorithm accompanies a comprehensive
explanation of the different stages of the algorithm.  The actions taken
during execution of the algorithm are described, followed by the process of
adding a new action.  The section concludes with an in-depth description of
the further complications and their solutions which complete the algorithm.

Section~\ref{parsing coverage} analyses the coverage the parser achieves
over a set of \numberOFlogFILES{} log files taken from a mail server
handling mail for over 1000 users.  Coverage is described both in terms of
the fraction of lines parsed and the fraction of mails and connections
successfully reconstructed by the parsing algorithm, including dealing with
false negatives and a discussion of the difficulties in identifying false
positives.  A random sampling of log lines are parsed, and the correctness
of the results manually verified, as part of determining the coverage of
the parser.

Section~\ref{limitations-improvements} lists the limitations of the
algorithm, then suggests some ways of dealing with them, with the goal of
improving parsing and reproduction of the journey a mail takes through
Postfix.

Section~\ref{conclusion} contains the paper's conclusion.

@@

The bibliography contains references to the resources used in developing
the algorithm, writing the program, and preparing this paper.  Also listed
are some additional resources expected to be helpful in understanding
\SMTP{}, Postfix, anti-spam techniques, or the paper.

Appendix~\ref{graphs} contains graphs illustrating the topics previously
discussed in \sectionref{rule efficiency}, rule efficiency, and explains
the irregularities observed in these graphs.

@@

    \item [\daemon{smtpd}, \daemon{postsuper}:] Mail accepted from a remote
        client, then deleted by the administrator before any delivery
        attempt (administrator deleting unwanted mail, typically due to a
        mail loop or joe-job).  Notice that \daemon{postsuper} is required,
        not optional, for this combination.
